### 2014-04-02 LaTeX/RhodiumEmp.tex

To estimate the model we use random effects clustered on countries and years. Results using a fixed effects estimation approach are similar. The model we estimate is shown below:

>>>>

To estimate the model we use random effects clustered on countries and years. Results using a fixed effects estimation approach are similar.\footnote{The fixed effects model includes the same regressors as the random effects model but adds indicator variables for each country in the sample.}  The model we estimate is shown below:
